null_model

### 2020-09-11 analysis/ts_null_model.Rmd
Remove old columns

trait_data <- biotime_traits %>% 
  select(-c(biotimeName, taxa, id_species, plot, year, year_abun, 
              year_biomass, traitName, scientificName, plot_id, study_id)) %>%
  distinct()

>>>>

trait_data <- sample_plots %>% 
  select(-c(biotimeName, taxa, id_species, plot, year, weight, 
            traitName, scientificName, plot_id, study_id)) %>%
  distinct()
